---
title: "Reproducible Research: Project 1"
output: 
  html_document:
    keep_md: true
---

```{r,echo=TRUE,results='hide'}
library(lubridate)
mydir<-getwd()
data<-file.path(mydir,"data","activity.csv")
```
## Code for reading in the dataset and/or processing the data
```{r,echo=TRUE}
df<-read.csv(data,stringsAsFactors = FALSE)
df$date<-as.Date(df$date,"%Y-%m-%d")
```

## Histogram of the total number of steps taken each day
```{r,echo=TRUE}
stps<- aggregate(df$steps, by=list(df$date), FUN=(sum))
names(stps)<-c("date","total")
plot(stps$date,stps$total,type="h",lwd="4",xlab="Date",ylab="Steps each day")
```

## Mean and median number of steps taken each day
```{r,echo=TRUE}
astps<- aggregate(df$steps, by=list(df$date), function(x) mean(x,na.rm=T))
names(astps)<-c("date","mean")
head(astps)


mstps<- aggregate(df$steps, by=list(df$date), function(x) median(x,na.rm=T))
names(mstps)<-c("date","median")
head(mstps)
```
## Time series plot of the average number of steps taken
```{r,echo=TRUE}
tsstps<- aggregate(df$steps, by=list(df$interval), function(x) mean(x,na.rm=T))
names(tsstps)<-c("interval","avg.steps")
plot(tsstps$interval,tsstps$avg.steps,ylab="Average Steps",xlab="Interval",type="l")
```

## The 5-minute interval that, on average, contains the maximum number of steps
```{r,echo=TRUE}
max(tsstps$avg.steps)
```

## Imputing missing values
```{r,echo=TRUE}
df1<-df
sum(is.na(df1$step))
df1[is.na(df1)] <- 0
nstps<- aggregate(df1$steps, by=list(df1$date), FUN=(sum))
names(nstps)<-c("date","total")
plot(nstps$date,nstps$total,type="h",lwd="4",xlab="Date",ylab="Steps each day")

nastps<- aggregate(df1$steps, by=list(df1$date), function(x) mean(x))
names(nastps)<-c("date","mean")
head(nastps)


nmstps<- aggregate(df1$steps, by=list(df1$date), function(x) median(x))
names(nmstps)<-c("date","median")
head(nmstps)

```

## Are there differences in activity patterns between weekdays and weekends?
```{r,echo=TRUE}
df2<-df1
df2$date <- as.POSIXlt(df2$date,format="%Y-%m-%d")
wkday<-subset(df2,df2$date$wday >=1 & df2$date$wday <= 5 )
wknda<-subset(df2,df2$date$wday >=6 & df2$date$wday <= 7 )

wkstps<- aggregate(wkday$steps, by=list(wkday$interval), FUN=(mean))
wkndstps<- aggregate(wknda$steps, by=list(wknda$interval), FUN=(mean))
names(wkstps)<-c("interval","avg.steps")
names(wkndstps)<-c("interval","avg.steps")
par(mfrow=c(2,1))
 plot(wkstps$interval,wkstps$avg.steps,ylab="Average Steps",xlab="Interval",type="l",col="blue",main="Weekdays")
 plot(wkndstps$interval,wkndstps$avg.steps,ylab="Average Steps",xlab="Interval",type="l",col="red",main="Weekend")
```
